\documentclass[11pt,letterpaper]{article}
\input{env.tex}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{multicol}

% Remove default spacing around title
\setlength{\droptitle}{-4em}

% % Custom title format
% \renewcommand{\maketitle}{
%     \begin{center}
%         {\huge\bfseries \@title}\\[0.5em]
%         {\large \@author}
%     \end{center}
% }

% Section formatting
\usepackage{sectsty}
\sectionfmt{\normalfont\bfseries}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1em}{0.5em}

% List formatting
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,topsep=0pt,itemsep=0.25em,parsep=0pt}

\title{Eric Yager}
\author{ericyager.com | \myEmail\ | \myPhoneNumber}
\date{}

\begin{document}

\maketitle

\vspace{-1em}
Results-driven Software Engineer with a comprehensive background in cloud-based backend development,
including microservices, monoliths, and serverless architectures. Proficient in Java, Python, Go, and TypeScript
with notable experience with AWS and Spring framework. Seeking to leverage deep technical skills and a
commitment to excellence in an individual contributor role, aiming to drive significant impacts through clean,
efficient codebases.

\section*{Experience}

\noindent\textbf{Cummins Inc.}, Indianapolis, IN\\
\noindent\textbf{Software Engineer} \hfill \textit{June 2022 -- present}
\begin{itemize}
    \item Scaled legacy Spring monolith to handle hundreds of daily requests and track process statuses.
    \item Investigated, debugged, and updated legacy Postgres stored procedures to handle new schemas.
    \item Synthesized requirements with input from stakeholders, including project managers and QA developers.
    \item Wrote unit and integration tests to ensure code quality as part of a test-driven development process.
    \item Collaborated in multiple intensive sprints to fix major production defects for a large telematics partner.
    \item Designed and implemented reusable common libraries in Java for use across applications.
    \item Developed new microservices, integrating with other services and relational \& document databases.
    \item Implemented JWT authentication \& authorization for integration with external partners.
    \item Created and deployed cloud resources using Infrastructure as Code and CI/CD pipelines.
\end{itemize}

\noindent\textbf{Software Engineering Intern} \hfill \textit{May 2021 -- August 2021}
\begin{itemize}
    \item Developed features and fixed bugs in web apps with Ktor and Node backends, and React frontends.
    \item Utilized version control and agile development practices to participate effectively on an agile team.
    \item Crafted DevSecOps implementation plan to prioritize security in the SDLC.
\end{itemize}

\noindent\textbf{Custom Machining Services, Continental AG}, Valparaiso, IN\\
\noindent\textbf{Software Engineering Intern} \hfill \textit{September 2021 -- May 2022}
\begin{itemize}
    \item Improved Android apps by adding UI elements and refactoring codebases to support multiple languages.
    \item Updated computer-generated reports to improve date formatting and include additional information.
    \item Collaborated with other engineers to test code on hardware, document bugs, and debug the codebase.
\end{itemize}

\section*{Education \& Certifications}

\noindent\textbf{AWS Certified Developer -- Associate} \hfill \textit{November 2024}
\begin{itemize}
    \item Proficient in developing, optimizing, deploying, and securing applications on AWS using CI/CD workflows.
    \item Able to identify and resolve application issues while ensuring code and data security.
\end{itemize}

\noindent\textbf{Bachelor of Science in Computer Science}, Valparaiso University, Valparaiso, IN \hfill \textit{May 2022}
\begin{itemize}
    \item 2\textsuperscript{nd} Major in Mathematics, minors in Data Science and Applied Statistics, 4.0/4.0 GPA
    \item Scholar of Christ College, the Interdisciplinary Honors College of Valparaiso University
    \item National Merit Scholar, and Louis A. Foster \& Martin David Mundt Awards recipient
    \item Putnam Math Competition: Achieved 74th percentile among exceptional undergraduate math students
    \item Association for Computing Machinery Chapter President, and Math Club Vice President
\end{itemize}

\section*{Skills}
\begin{multicols}{3}
\begin{itemize}
    \item Java \& JavaFX
    \item Git, Github
    \item Unix, GNU/Linux
    \item Chrome Extensions
    \item Python 2 \& 3
    \item HTML \& CSS
    \item X86 Assembly
    \item Ruby \& Ruby on Rails
    \item JavaScript
    \item Arena Simulation Tool
    \item PHP \& Wordpress
    \item Google G Suite Scripts
    \item Go/Golang
    \item Netlogo Modeling System
    \item AngularJS
    \item Amazon Web Services
    \item React.js
    \item Scala
    \item Kotlin
    \item Ktor
    \item Spring Framework
    \item JUnit 4 \& 5
    \item Bash \& Zsh Scripting
    \item Node.js
\end{itemize}
\end{multicols}

\end{document}